outline!

### 2016-05-24 paper.tex
paper updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\lstset{frame=tb,
  language=Ruby,
  captionpos=b,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\scriptsize\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  %keywordstyle=\color{blue},
  %commentstyle=\color{dkgreen},
  %stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

\begin{lstlisting}[caption={Hello}, label=lab]
class Corfu
include Bud

state do
table :epoch, [:epoch]
table :log, [:pos] => [:state, :data]

scratch :valid_op, [:type, :pos, :epoch] => [:data]
scratch :invalid_op, [:type, :pos, :epoch] => [:data]

interface input, :op, [:type, :pos, :epoch] => [:data]
interface output, :ret, [:type, :pos, :epoch] => [:retval]
end
\end{lstlisting}

>>>>

\lstset{frame=tb,
  language=Ruby,
  captionpos=b,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  %columns=flexible,
  basicstyle={\scriptsize\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  %keywordstyle=\color{blue},
  %commentstyle=\color{dkgreen},
  %stringstyle=\color{mauve},
  %breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

@@

\begin{lstlisting}[caption={Epoch Guard}, label=lst:eg]
bloom :epoch_guard do
  invalid <= (op * epoch).pairs{|o,e| o.epoch <= e.epoch}
  ret <= invalid{|o| [o.type, o.pos, o.epoch, 'stale']}
  valid <= op.notin(invalid)
end
\end{lstlisting}
